The Impact of Alternation

### 2017-05-14 draft.tex
ok

\begin{figure}[htb]
\begin{tabular}{cc}
\includegraphics[scale=0.5]{figures/PA1.pdf} & \includegraphics[scale=0.5]{figures/PA2.pdf} \\
\footnotesize{(a)} & \footnotesize{(b)} \\
\\
\includegraphics[scale=0.5]{figures/PA3.pdf} & \includegraphics[scale=0.5]{figures/PA4.pdf} \\
\footnotesize{(c)} & \footnotesize{(d)}
\end{tabular}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex} using Algorithm \ref{alg:predabs}}
\label{fig:pa}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{tabular}{cc}
\includegraphics[scale=0.52]{figures/PA1.pdf} & \includegraphics[scale=0.52]{figures/PA2.pdf} \\
\footnotesize{(a)} & \footnotesize{(b)} \\
\\
\includegraphics[scale=0.52]{figures/PA3.pdf} & \includegraphics[scale=0.52]{figures/PA4.pdf} \\
\footnotesize{(c)} & \footnotesize{(d)}
\end{tabular}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex} using Algorithm \ref{alg:predabs}}
\label{fig:pa}
\end{figure}
